---
title: "Introduction to FARS"
author: "Manuel"
date: "2020-11-26"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The FARS R package provides functionality to read, analyze and visualize data
acquired from the databases of the US National Highway Traffic Safety
Administration's Fatality Analysis Reporting System (FARS).

## fars_read_years
This function reads the data from existing FARS files for each of the years
provided in an input argument as a vector containing a set of 4-digit years. The
function returns a list of data, with one element for each year, each being a
tibble with that year's FARS data. Example:
```{r, eval=FALSE}
fars_read_years(2015)
fars_read_years(years = c(2013:2015)
```


## fars_summarize_years
This function reads the data from existing FARS files for each of the years
provided in an input argument as a vector containing a set of 4-digit years. The
function returns a tibble containing a monthly summary of the FARS data for each
of the requested years of the FARS database. Example:
```{r, eval=FALSE}
fars_summarize_years(2015)
fars_summarize_years(years = c(2013:2015))
```


## fars_map_state
This function reads the data from existing FARS files for the requested year and
plots a map with the FARS data for the requested state and year. Example:
```{r, eval=FALSE}
fars_map_state(12,2015)
fars_map_state(state.num = 12,year = 2015)
```
